The limits of self commitment and private paternalism \thanks{}

### 2020-06-18 main.tex
preparation for first draft

\title{Private paternalism and the limits of self commitment  \thanks{We want to thank Craig McIntosh and Mauricio Romero for advice and encouragement. We want to thank also Ricardo Olivares for excellent research assistance and Erik Molina help with formatting. Jose Maria Barrero, Emilio Gutierrez, Aprajit Mahajan, Matt Rabin and seminar participants at ITAM provided very valuable feedback.}}
\author{Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx;  
Seira: ITAM, enrique.seira@itam.mx} }
\date{This draft:  \today \\[2 cm]}

@@

Indeed, using a survey conducted by us in branches of Lender $P$, we document some evidence consistent with regulators' concerns: while pawnshop clients predict they will recover their pawn with 93\% probability on average, in reality only 44\% of them do, suggesting naivete. Even conditional on paying a positive amount towards pawn recovery, 47\% lose their pawn and their payment. In our survey 69\% report self-control problems saying they often fall into temptation spending. %, but only \hlgr{15\%} show inter-temporal inconsistencies in a classical present-bias question, a similar number to \cite{Ashaf}. %and \hl{19\%} do not normally budget monthly expenses. 
%While this is suggestive of a present bias problem or overconfidence to save and pay, at the same time our subjects are experienced and not wholly uneducated, 66\% have completed at least high school and 90\% have pawned before. %and \hl{38\%} have participated in a Rosca.

@@

We find that forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more. The effects are large: financing cost decreases by 9.5\% on average, while the likelihood of recovering their pawn increases by 25.8\%. Results are robust to including in the cost definition transport costs of going to the branch plus losing a day's wage for each visit. Importantly, the benefits are distributed broadly: the whole distribution of treatment effects shows cost savings. The most economically vulnerable, those that report being stressed, and those that asked for a reminder at baseline, experience the largest financial cost savings. Those we classify as present biased and those that requested a reminder at baseline experience the largest effects on pawn recovery. %The commitment contract also causes payments to start 8 days earlier and be 16\% more frequent, compared to the control group. 
Treatment effects are concentrated on the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. It seems that the fee-commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost. Finally, we find that borrowers assigned to the forced fee-commitment contract are 5pp (55\% of the mean) more likely to be repeat costumers than the control group, suggesting that they themselves liked the commitment contract more after experiencing it.

@@

How much money is left on the table by the prevalence of the status-quo choice? We calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost. On average they spend an extra \$238 pesos, close to 12\% of the average loan value. In particular 92\% of those that chose the status-quo contract would have been better in the fee-commitment contract, while only 8\% of those who chose the fee-commitment contract would have been better in the status-quo one. This suggests that forcing clients into commitment contacts (i.e. private paternalism) may be welfare increasing for the overwhelming majority of clients.

@@

One potential explanation for high default is that clients are really just selling their gold piece. This is unlikely for severalreasons: (a)  the reported subjective value of the pawn is larger than the loan size for \hl{86\%} of them, (b) among those that lose their pawn 74\% paid a positive amount towards its recovery --- this can only be rationalized if they expected to recover their pawn, (c) it is typical to find gold purchasing stores close to where the pawnshops are located (see Figure \ref{GoldBuyers}) and they give more than what Lender P gives for the pawn, (d) there is a lot of engagement with the lender after pawning even for those who lost their pawn. On average clients that lost their pawn paid 34\% of the value of their loan, and close to 55\% of clients extended the loan for another cycle and made payments in the second cycle (see Figure \ref{proxy_naive} in Appendix).

@@

We had a team of ITAM student enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients. The enumerators were inside the branch and asked clients to complete a short 5 minutes survey before going to the teller window to appraise their piece. The survey was necessarily short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if the family or friends commonly asked for money, how time consuming and costly was to come to the branch, the subjective probability of recovering their piece that they intended to pawn, the subjective value of their piece in money terms (for how much money would they sell it for), among others. We were able to survey 7,704 clients (some refused). %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}. 
The appendix \ref{baseline_survey} transcribes the questionnaire in English and presents summary stats. Survey response rate is 57\%, the Appendix Table \ref{balance_response} shows that response is not related to admin data observables.

@@

Table \ref{SS} presents some summary statistics for the whole sample and by treatment arm. Because treatment arms are described below, here we concentrate on the overall average. Panel A describes variables from the administrative data. It shows that the average loan size is \$1945 pesos (\$105 usd). The average number of pawns per day per branch is 33. Although not shown in the table, only 40\% of clients recover they pawn within 230 days. Even those that recover their pawn tend to pay it back at the last moment, with only 17\% paying before the 90th day.

@@

Since the main treatment involves making clients come to the branch to pay each month, the transaction costs of coming to the branch are important, and we ask two questions about them. The average time they take to come to the branch is 22 minutes, and the amount of money they spend in transport to do that is 11 pesos (\$0.60 usd).  
The population we are working with is economically vulnerable in the sense that 31\% of them could not pay either water, electricity \& gas or rent in the past 6 months. They often receive negative income shocks: 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a `non-urgent expense'.
%When asked why they are pawning this piece \hlgr{5\%} responded \hlgr{`lost a family member'}, \hlgr{`a medical emergency'} (\hlgr{11\%}), \hlgr{`an urgent expense'} (\hlgr{71\%}),

@@

We define financial cost as the discounted sum of payments toward the loan plus the value of the pawn, and subtract the subjective discounted value of the pawn when it is recovered: $Financial \; Cost_i = \sum_t \frac{P_{it}}{(1+r)^t} + Pawn \: Value_i - \frac{\text{I}(Recovered \: Pawn_i) \times Pawn \: Value_i}{(1+r)^T}$, with $t$ indexing days, $T$ is the day when the pawn is recovered, I($\cdot$) an indicator function for recovering the pawn, $r$ is a daily interest rate equivalent to a 7\% monthly interest rate.\footnote{We experimented with different interest rates with similar results. See section \ref{neoclasical}.} Figure \ref{fc_hist}(a) plots a histogram of this cost in pesos for loans where the pawn was recovered or lost. This cost is calculated for a time period of 230 days after loan origination, as 50\% of clients actually renew the loan one time. Of those who renew 34\% lose the pawn. Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn.  Panel (b) normalizes the cost by loan size. It shows that as a percentage of their pawn, most of the cost comes from clients that do not recover their pawn. For them the cost is between 140\% and 250\% of the loan value. %\hl{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.} 
We calculate an APR of \hl{177\% on average for the control group.}\footnote{The Annual Percentage Rate (for pawn $j$) is calculated as the internal rate of return $i$ such that $\sum_t \frac{P_{jt}}{(1+i)^t} + \frac{\text{I}(Default \: Pawn_j) \times Pawn \: Value_j}{(1+i)^T} - Pawn \: Value_j = 0$, where $T$ is the date the pawn was lost.}

@@

\noindent \textbd{Selection of branches.} Starting September 6th 2012, we implemented our experiment in 6 branches of Lender $P$. The branches were selected by Lender $P$ to be dispersed across Mexico city and have varying sizes. In four of them the experiment ran for 107 days, and in 2 of them we ran it for a shorter time to economize on data collection costs since we realized we would not be constrained by sample size. %Thus we eliminated \hl{the smallest} ones. 
Branches are more than 5 km apart from each other, and there is little substitution among them (only 1\% of consumers appear in more than one of our branches).

\vspace{.2in}
\noindent \textbf{The monthly installment contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract in all respects except one. It has the same interest rate (7\% \textit{per month} which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days, and a grace period of 15 days), and the gold pawn gets appraised in the same way by the same appraisers. The only difference is that it has a requirement that the client has to pay monthly: for the 3 month duration at least 1/3 of the loan value (plus accumulated interest) has to be paid before day 30th, 60th and 90th after loan disbursement. Failure to pay this amount triggers a penalty fee of 2\% of this minimum amount due, which is added to the amount that the client needs to pay to recover their pawn. This penalty acts as a commitment incentive to pay now vs paying later. The level of the penalty was determined by Lender $P$ after talking to clients and based on Lender $P$'s experience. They deemed 2\% something that was big enough to provide commitment but small enough that if clients had an emergency and could not pay, the fee would not cause the pawn to be unrecoverable.\footnote{In contrast with \cite{John} we don't let the clients choose the size of the fee. As that paper shows doing this results in wrong choices by naive present biased consumers. Our fee is much smaller than the median in her experiment as explained above. We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.}

@@

\noindent where $i$ refers to client, $j$ indexes branch, and $X_{ij}$ are branch and day-of-week fixed effects.\footnote{There is a minority of of clients that pawned again and got assigned a different treatment. Results are robust to excluding them. In the regressions we include them and add a dummy indicating who are these clients.} %\footnote{There If we restrict ourselves to pieces that fall in a single-arm (64\%), then treatment reduces the financial cost by 5.7\%, increases the likelihood of recovering their pawn by 35\%, and increases the likelihood of repeat business by 66\%.}.
Our main outcome variables $y_{ij}$ are measures of financial cost in pesos as defined in Section \ref{FC_def}, as well as an indicator variable for client $i$ losing her pawn. In this subsection $T_{i}$ is an indicator for $i$ having got the \textit{fee-forcing} contract, and $\beta$ estimates the average treatment effect.%\footnote{This is an ATE and not just an ITT since take up of treatment is 100\%.}

\vspace{.2in}
\noindent \textbf{Financial Cost.} Figure \ref{fc_pro2}(a) reports $\beta$ coefficients and their 95\% confidence interval from estimating equation (\ref{basic_reg}) using different definitions of financial cost. The leftmost coefficient corresponds to using the appraised gold value of the pawned piece (not discounting makes virtually no difference). The second coefficient uses the subjective value of the pawn instead. In both cases we find that being assigned to the fee-forcing commitment contract causes a large reduction in the financing cost the client incurred, of 9.5\% (\hl{\$XXX}) in the fist definition and 13.3\% (\hl{\$XXX}) in the second one. That is, we find that \textit{charging} clients a late payment fee  actually decreases total \textit{fee-inclusive} financing cost.

@@

\vspace{.2in}
\noindent \textbf{Pawn Recovery.} Figure \ref{fc_pro2}(d) plots estimated treatment effects of the fee-forcing commitment contract with the dependent variable being an indicator of losing the pawn in less than 230 days. The leftmost coefficient shows that the fee-forcing commitment contract increases the likelihood of recovering the pawn by 11pp (25.8\% of mean recovery). This is a large effect. It contrasts for instance with \cite{Pande} who find no effect of payment frequency on default in a group lending microfinance context. Figure \ref{fc_pro2}(e) shows the distribution of heterogeneous treatment effects for losing pawn: it shows that \textit{everybody's} likelihood of losing the pawn decreases. %Figure \ref{HTE_fee_forcing}(b) in the Appendix shows that those we classify as present biased, those that requested to be sent a reminder to pay, and those who have more problems paying for basic services experienced the largest increases on pawn recovery.

@@

\vspace{.2in}
\noindent \textbf{Effects on other outcomes.} There are other (intermediate) outcomes that are impacted by being assigned to frequent payments. Table \ref{mechanisms} shows that the first payment happens 8 days earlier (column 1) in the fee-forcing arm than in the status quo one, and that the number of payments increases by 0.19 (column 2). Figure \ref{induced_to_pay_early} in the Appendix correlates heterogeneous treatment effects on financing cost and time of first payment and shows that those induced to pay earlier are also those that have larger induced savings in financial cost. A second finding is that treatment effects are concentrated on the intensive margin, as treatment does \textit{not} affect the fraction of clients who pay a positive amount (column 6). The percentage of the loan paid increases by 8 percentage points on average (column 7). Note however is that the percentage of the loan paid is not larger for those that end up losing the pawn (first row of column 8).

\vspace{.2in}
\noindent \textbf{Other sub-samples.} Going back to Figure \ref{fc_pro2}(a), we estimate some interesting correlations. The 4th coefficient from left to right conditions on those who paid a positive amount (in treatment and control). Although this is potentially an endogenous population, Table \ref{mechanisms} showed that there is no treatment effect on Pay$>0$. We were interested in this population to show that the effect is there for those who are serious about recovering their pawn. The fifth coefficient conditions on those that paid a fee in the fee-forcing group. In effect comparing this subset in treatment vs all of the control group\footnote{Results are similar if we condition in the control group on those who would have paid a fee given current behavior. Again we acknowledge these is an endogenous control and that the estimate is not a causal effect.}. We find even those that paid a fee in the fee-forcing contract end up paying a smaller financial cost that those in the status-quo contract.\footnote{This is not an experimental comparison as who pays a fee in the treatment group is a selected sample, but we found this relationship interesting nonetheless.} Figure \ref{fc_pro2}(c) shows that the increase in pawn recovery is robust to defining recovery using the first 120 days of the contract, or restricting to those paying a positive amount towards pawn recovery.

@@

We have shown that clients are more likely to recover their pawn that virtually all of them incur in a lower financial cost  when assigned a monthly payment commitment contract with fees. This however does not necessarily show that they benefited in utility terms, and this is hard to show directly. If ---as suggested by \cite{Laibson2018}--- consumers used ``experienced utility'' as a guide to make future purchases, we conjecture that clients in the fee-forcing contract would be more likely to be repeat costumers vis-a-vis those that got status quo contract. This is indeed what we find.

Figure \ref{reincidence} presents results of equation (\ref{basic_reg}) where the dependent variable is a dummy for the client to be a repeat costumer. We define a client in our experiment as a repeat costumer if, after experiencing at least 75 days of the respective treatment arm, she came back and pawned a different piece.\footnote{Results are robust to using other number of days besides 75.}  The left most coefficient shows that the causal effect of the fee-forcing contract on repeat pawning is an increase of 5pp in the probability of being a repeat costumer, this is 55\% on a mean re-incidence in the control group, with respect to those that got the status-quo contract. This is not explained by clients recovering their first pawn with higher probability in the fee-forcing contract and re-pawning this same one since we make sure it is another piece (besides only 37\% recover their piece in the fist 75 days in the fee forcing contract). The second coefficient restricts to the population who had larger (treatment effect) financial cost savings in their first pawn, and shows that the effect is twice as large for them. That is, those that benefit more from the fee-forcing contract are much more likely to repeat. %The coefficient on repeat pawning is just as big when we focus only 2nd pawns happening after the first was recovered (third coefficient ``fnr'').  This is consistent with \cite{Laibson2018}'s conjecture that clients could be making decisions based on experienced utility.\footnote{The third coefficient conditions on the subsample that did recover their first pawn in both arms and finds a coefficient of 4pp. This is not a causal estimate as recovery is influenced by treatment, but we found it telling that the differences were similar to the causal estimate for the full sample.}

We also implemented an exit survey which clients filled when recovering their piece. Unfortunately it had low response rates (7\%), and we take its results with a grain of salt. In this survey 63\% said they liked the frequent payment contract more than the status-quo one, and that is allow them avoid unnecessary expenses.

@@

Section \ref{fee-commitment} showed that the fee-forcing commitment contract reduced financing cost across the board, and that consumers themselves seemed to like it once they tried it. In such a case, one would expect a strong demand for it, unless consumers underestimated these benefits.

@@

To study demand for commitment, in one experimental arm, we let clients freely choose between the two types of contract: the fee-forcing commitment contract or the status-quo contract. The first result here is that in spite of broadly distributed benefits of the fee-forcing commitment contract we documented above, 90\% of clients chose \textit{not} to have it, they instead preferred the status-quo one. As explained above we are fairly confident this was not because a lack of understanding of the contracts.

What can explain this low demand? This section discusses some hypothesis but lack of data limits what can be tested. One neoclassical explanation could be risk. Even if the fee forcing contract generates cost savings on average, clients with risk averse preferences may not demand it if they perceive higher risk from it.\footnote{Because they have not experienced the fee-forcing contract before, ambiguity aversion may play a role here too.} Alternatively, even risk-neutral agents may not demand it if the cost of lost flexibility is high. If they for example face large and frequent income shocks which make it hard to repay monthly.\footnote{We don't observe income shocks in our data, making is hard to quantify how important they are. 90\% of those in the fee-forcing arm incurred a fee, which suggests that shocks are not uncommon (or clients inattentive).} Below we focus on some explanations of low demand, while Section \ref{model} seeks for theories that can explain all the findings, and reaches the conclusion that the present bias with naivete parsimoniously explains more results.

\subsubsection{Behavioral economics explanations} \label{behavioral}

>>>>

\title{Private paternalism and the limits of self commitment  \thanks{We want to thank Craig McIntosh and Mauricio Romero for advice and encouragement. We want to thank also Ricardo Olivares for excellent research assistance and Erick Molina help with formatting. Jose Maria Barrero, Emilio Gutierrez, Aprajit Mahajan, Matt Rabin, and seminar participants at ITAM provided very valuable feedback.}}
\author{Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx;  
Seira: ITAM, enrique.seira@itam.mx} }
\date{This draft:  \today \\[2 cm]}

@@

Indeed, using a survey conducted by us in branches of Lender $P$, we document some evidence consistent with regulators' concerns: while pawnshop clients predict they will recover their pawn with 93\% probability on average, in reality only 40\% of them do, suggesting naivete. Even conditional on paying a positive amount towards pawn recovery, 53\% lose their pawn and their payment. In our survey 69\% report self-control problems saying they often fall into temptation spending. %, but only \hlgr{15\%} show inter-temporal inconsistencies in a classical present-bias question, a similar number to \cite{Ashaf}. %and \hl{19\%} do not normally budget monthly expenses. 
%While this is suggestive of a present bias problem or overconfidence to save and pay, at the same time our subjects are experienced and not wholly uneducated, 66\% have completed at least high school and 90\% have pawned before. %and \hl{38\%} have participated in a Rosca.

@@

We find that forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more. The effects are large: financing cost decreases by 9.5\% on average, while the likelihood of recovering their pawn increases by 25\%. Results are robust to including in the cost definition transport costs of going to the branch plus losing a day's wage for each visit. Importantly, the benefits are distributed broadly: the whole distribution of treatment effects shows cost savings. The most economically vulnerable, those that report being stressed, and those that asked for a reminder at baseline, experience the largest financial cost savings. Those we classify as present biased and those that requested a reminder at baseline experience the largest effects on pawn recovery. %The commitment contract also causes payments to start 8 days earlier and be 16\% more frequent, compared to the control group. 
Treatment effects are concentrated on the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. It seems that the fee-commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost. Finally, we find that borrowers assigned to the forced fee-commitment contract are 5pp (55\% of the mean) more likely to be repeat costumers than the control group, suggesting that they themselves liked the commitment contract more after experiencing it.

@@

How much money is left on the table by the prevalence of the status-quo choice? We calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost. On average they spend an extra \$238 pesos, close to 11\% of the average loan value. In particular 92\% of those that chose the status-quo contract would have been better in the fee-commitment contract, while only 8\% of those who chose the fee-commitment contract would have been better in the status-quo one. This suggests that forcing clients into commitment contacts (i.e. private paternalism) may be welfare increasing for the overwhelming majority of clients.

@@

One potential explanation for high default is that clients are really just selling their gold piece. This is unlikely for several reasons: (a)  the reported subjective value of the pawn is larger than the loan size for \hl{86\%} of them, (b) among those that lose their pawn 58\% paid a positive amount towards its recovery --- this can only be rationalized if they expected to recover their pawn, (c) it is typical to find gold purchasing stores close to where the pawnshops are located (see Figure \ref{GoldBuyers}) and they give more than what Lender P gives for the pawn, (d) there is a lot of engagement with the lender after pawning even for those who lost their pawn. On average clients that lost their pawn paid 34\% of the value of their loan, and close to 42\% of clients extended the loan for another cycle and made payments in the second cycle (see Figure \ref{proxy_naive} in Appendix).

@@

We had a team of ITAM student enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients. The enumerators were inside the branch and asked clients to complete a short 5 minutes survey before going to the teller window to appraise their piece. The survey was necessarily short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if the family or friends commonly asked for money, how time consuming and costly was to come to the branch, the subjective probability of recovering their piece that they intended to pawn, the subjective value of their piece in money terms (for how much money would they sell it for), among others. We were able to survey 7,704 clients (some refused). %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}. 
The appendix \ref{baseline_survey} transcribes the questionnaire in English \hl{and presents summary stats}. Survey response rate is 57\%, the Appendix Table \ref{balance_response} shows that response is not related to admin data observables.

@@

Table \ref{SS} presents some summary statistics for the whole sample and by treatment arm. Because treatment arms are described below, here we concentrate on the overall average. Panel A describes variables from the administrative data. It shows that the average loan size is \$2171 pesos (\$105 usd). The average number of pawns per day per branch is 33. Although not shown in the table, only 40\% of clients recover they pawn within 230 days. Even those that recover their pawn tend to pay it back at the last moment, with only 17\% paying before the 90th day.

@@

Since the main treatment involves making clients come to the branch to pay each month, the transaction costs of coming to the branch are important, and we ask two questions about them. The average time they take to come to the branch is 22 minutes, and the amount of money they spend in transport to do that is 11 pesos (\$0.60 usd).  
The population we are working with is economically vulnerable in the sense that 30\% of them could not pay either water, electricity \& gas or rent in the past 6 months. They often receive negative income shocks: 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a `non-urgent expense'.
%When asked why they are pawning this piece \hlgr{5\%} responded \hlgr{`lost a family member'}, \hlgr{`a medical emergency'} (\hlgr{11\%}), \hlgr{`an urgent expense'} (\hlgr{71\%}),

@@

We define financial cost as the discounted sum of payments toward the loan plus the value of the pawn, and subtract the subjective discounted value of the pawn when it is recovered: $Financial \; Cost_i = \sum_t \frac{P_{it}}{(1+r)^t} + Pawn \: Value_i - \frac{\text{I}(Recovered \: Pawn_i) \times Pawn \: Value_i}{(1+r)^T}$, with $t$ indexing days, $T$ is the day when the pawn is recovered, I($\cdot$) an indicator function for recovering the pawn, $r$ is a daily interest rate equivalent to a 7\% monthly interest rate.\footnote{We experimented with different interest rates with similar results. See section \ref{neoclasical}.} Figure \ref{fc_hist}(a) plots a histogram of this cost in pesos for loans where the pawn was recovered or lost. This cost is calculated for a time period of 230 days after loan origination, as 60\% of clients actually renew the loan one time. Of those who renew 83\% lose the pawn. Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn.  Panel (b) normalizes the cost by loan size. It shows that as a percentage of their pawn, most of the cost comes from clients that do not recover their pawn. For them the cost is between 140\% and 250\% of the loan value. %\hl{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.} 
We calculate an APR of \hl{177\% on average for the control group.}\footnote{The Annual Percentage Rate (for pawn $j$) is calculated as the internal rate of return $i$ such that $\sum_t \frac{P_{jt}}{(1+i)^t} + \frac{\text{I}(Default \: Pawn_j) \times Pawn \: Value_j}{(1+i)^T} - Pawn \: Value_j = 0$, where $T$ is the date the pawn was lost.}

@@

\noindent \textbf{Selection of branches.} Starting September 6th 2012, we implemented our experiment in 6 branches of Lender $P$. The branches were selected by Lender $P$ to be dispersed across Mexico city and have varying sizes. In four of them the experiment ran for 107 days, and in 2 of them we ran it for a shorter time to economize on data collection costs since we realized we would not be constrained by sample size. %Thus we eliminated \hl{the smallest} ones. 
Branches are more than 5 km apart from each other, and there is little substitution among them (only 1\% of consumers appear in more than one of our branches).

\vspace{.2in}
\noindent \textbf{The monthly installment contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract in all respects except one. It has the same interest rate (7\% \textit{per month} which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days, and a grace period of 15 days), and the gold pawn gets appraised in the same way by the same appraisers. The only difference is that it has a requirement that the client has to pay monthly: for the 3 month duration at least 1/3 of the loan value (plus accumulated interest) has to be paid before day 30th, 60th and 90th after loan disbursement. Failure to pay this amount triggers a penalty fee of 2\% of this minimum amount due, which is added to the amount that the client needs to pay to recover their pawn. This penalty acts as a commitment incentive to pay now vs paying later. The level of the penalty was determined by Lender $P$ after talking to clients and based on Lender $P$'s experience. They deemed 2\% something that was big enough to provide commitment but small enough that if clients had an emergency and could not pay, the fee would not cause the pawn to be unrecoverable.\footnote{In contrast with \cite{John} we don't let the clients choose the size of the fee. As that paper shows doing this results in wrong choices by naive present biased consumers. \hl{Our fee is much smaller than the median in her} experiment as explained above. We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.}

@@

\noindent where $i$ refers to client, $j$ indexes branch, and $X_{ij}$ are branch and day-of-week fixed effects.\footnote{There is a minority of of clients that pawned again and got assigned a different treatment. Results are robust to excluding them. In the regressions we include them and add a dummy indicating who are these clients.} %\footnote{If we restrict ourselves to pieces that fall in a single-arm (64\%), then treatment reduces the financial cost by 5.7\%, increases the likelihood of recovering their pawn by 35\%, and increases the likelihood of repeat business by 66\%.}.
Our main outcome variables $y_{ij}$ are measures of financial cost in pesos as defined in Section \ref{FC_def}, as well as an indicator variable for client $i$ losing her pawn. In this subsection $T_{i}$ is an indicator for $i$ having got the \textit{fee-forcing} contract, and $\beta$ estimates the average treatment effect.%\footnote{This is an ATE and not just an ITT since take up of treatment is 100\%.}

\vspace{.2in}
\noindent \textbf{Financial Cost.} Figure \ref{fc_pro2}(a) reports $\beta$ coefficients and their 95\% confidence interval from estimating equation (\ref{basic_reg}) using different definitions of financial cost. The leftmost coefficient corresponds to using the appraised gold value of the pawned piece (not discounting makes virtually no difference). The second coefficient uses the subjective value of the pawn instead. In both cases we find that being assigned to the fee-forcing commitment contract causes a large reduction in the financing cost the client incurred, of 9.5\% (\hl{\$304}) in the fist definition and 13.3\% (\hl{\$478}) in the second one. That is, we find that \textit{charging} clients a late payment fee  actually decreases total \textit{fee-inclusive} financing cost.

@@

\vspace{.2in}
\noindent \textbf{Pawn Recovery.} Figure \ref{fc_pro2}(d) plots estimated treatment effects of the fee-forcing commitment contract with the dependent variable being an indicator of losing the pawn in less than 230 days. The leftmost coefficient shows that the fee-forcing commitment contract increases the likelihood of recovering the pawn by 11pp (25\% of mean recovery). This is a large effect. It contrasts for instance with \cite{Pande} who find no effect of payment frequency on default in a group lending microfinance context. Figure \ref{fc_pro2}(e) shows the distribution of heterogeneous treatment effects for losing pawn: it shows that \textit{everybody's} likelihood of losing the pawn decreases. %Figure \ref{HTE_fee_forcing}(b) in the Appendix shows that those we classify as present biased, those that requested to be sent a reminder to pay, and those who have more problems paying for basic services experienced the largest increases on pawn recovery.

@@

\vspace{.2in}
\noindent \textbf{Effects on other outcomes.} There are other (intermediate) outcomes that are impacted by being assigned to frequent payments. Table \ref{mechanisms} shows that the first payment happens 8 days earlier (column 1) in the fee-forcing arm than in the status quo one, and that the number of payments increases by 0.19 (column 2). Figure \ref{induced_to_pay_early} in the Appendix correlates heterogeneous treatment effects on financing cost and time of first payment and shows that those induced to pay earlier are also those that have larger induced reduction in financial cost. A second finding is that treatment effects are concentrated on the intensive margin, as treatment does \textit{not} affect the fraction of clients who pay a positive amount (column 6). The percentage of the loan paid increases by 8 percentage points on average (column 7). Note however is that the percentage of the loan paid is not larger for those that end up losing the pawn (first row of column 8).

\vspace{.2in}
\noindent \textbf{Other sub-samples.} Going back to Figure \ref{fc_pro2}(a), we estimate some interesting correlations. The 4th coefficient from left to right conditions on those who paid a positive amount (in treatment and control). Although this is potentially an a selected subsample, Table \ref{mechanisms} showed that there is no treatment effect on pay$>0$. We were interested in this population to show that the effect is there for those who are serious about recovering their pawn. The fifth coefficient conditions on those that paid a fee in the fee-forcing group, comparing this subset in treatment vs all of the control group.\footnote{Results are similar if we condition in the control group on those who would have paid a fee given current behavior. Again we acknowledge these is an endogenous sample and that the estimate may not be a causal effect.} We find that even those that paid a fee in the fee-forcing contract end up paying a smaller financial cost that those in the status-quo contract. Figure \ref{fc_pro2}(c) shows that the increase in pawn recovery is robust to defining recovery using the first 120 days of the contract, or restricting to those paying a positive amount towards pawn recovery.

@@

We have shown that all clients are more likely to recover their pawn and almost all of them incur in a lower financial cost  when assigned to a monthly payment commitment contract. This however does not necessarily show that they benefited in utility terms, and this is hard to show directly. If ---as suggested by \cite{Laibson2018}--- consumers used ``experienced utility'' as a guide to make future purchases, we conjecture that clients in the fee-forcing contract would be more likely to be repeat costumers vis-a-vis those that got status quo contract. This is indeed what we find.

Figure \ref{reincidence} presents results of equation (\ref{basic_reg}) where the dependent variable is a dummy for the client being a repeat costumer. We define a client as a repeat costumer if, after experiencing at least 75 days of the respective treatment arm, she came back and pawned a \textit{different} piece.\footnote{Results are robust to using other number of days besides 75. We know its a different piece from them having a different weight.}  The left most coefficient shows that the causal effect of the fee-forcing contract on repeat pawning is an increase of 5pp in the probability of being a repeat costumer, this is 55\% increase on a mean re-incidence with respect to those that got the status-quo contract. This effect is not explained by clients recovering their first pawn with higher probability in the fee-forcing contract and re-pawning this same one since we make sure it is another piece (only \hl{16\%} recover their piece in the fist 75 days in the fee forcing contract). The second coefficient restricts the sample in the regression to those that had not recovered their pawn in the first 75 days and finds similar result. Finally, the third coefficient focuses on the subsample who experienced a financial cost savings treatment effect above the median treatment effect in their first pawn. It shows that for these clients the likelihood of coming back is twice as large (although imprecise). That is, those that benefit more from the fee-forcing contract are more likely to repeat.\footnote{We also implemented an exit survey which clients filled when recovering their piece. Unfortunately it had low response rates (7\%), and we take its results with a grain of salt. In this survey 63\% said they liked the frequent payment contract more than the status-quo one, and that is allow them avoid unnecessary expenses.} %The coefficient on repeat pawning is just as big when we focus only 2nd pawns happening after the first was recovered (third coefficient ``fnr'').  This is consistent with \cite{Laibson2018}'s conjecture that clients could be making decisions based on experienced utility.\footnote{The third coefficient conditions on the subsample that did recover their first pawn in both arms and finds a coefficient of 4pp. This is not a causal estimate as recovery is influenced by treatment, but we found it telling that the differences were similar to the causal estimate for the full sample.}

@@

Section \ref{fee-commitment} showed that the fee-forcing commitment contract reduced financing cost across the board, and that consumers themselves seemed to like it once they tried it. In such a case, one would expect a strong demand for it.

@@

To study demand for commitment, in one experimental arm, we let clients freely choose between the two types of contract: the fee-forcing commitment contract or the status-quo contract. In spite of broadly distributed benefits of the fee-forcing commitment contract we documented above, 90\% of clients chose \textit{not} to have it, they instead preferred the status-quo one. As explained above we are fairly confident this was not because a lack of understanding of the contracts.

What can explain this low demand? This section discusses some hypothesis but data limits what can be tested. One neoclassical explanation could be risk. Even if the fee forcing contract generates cost savings on average, clients with risk averse preferences may not demand it if they perceive higher risk from it.  Alternatively, even risk-neutral agents may not demand it if the cost of lost flexibility is high. If clients, for instance, face large and frequent income shocks which make it hard to repay monthly.\footnote{We don't observe income shocks in our data, making is hard to quantify how important they are. 91\% of those in the fee-forcing arm incurred a fee, which suggests that shocks are not uncommon.} Below we focus on some explanations of low demand, while Section \ref{model} seeks theories that can explain all the findings at the same time.

\subsubsection{Behavioral explanations} \label{behavioral}

The leading behavioral explanation in the literature for low demand for commitment is present biased preferences with naivete (e.g. \cite{Rabin2018}, \cite{John}, \cite{Laibson2018})  \cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can limit take-up especially severely when agents are naive about their self control problem. In our context if consumers are naive about their present bias, they would plan to save more (or spend less) than what they actually end up saving, thus making it be harder to recover their pawn. This under-saving will be mitigated in the fee forcing contract since the fee makes them save money to pay part of the loan periodically. Section \ref{model} formalizes this in a model. Another behavioral explanation is that clients may underestimate the likelihood and severity of negative income shocks. Both of these explanations predict that clients will be overconfident about their likelihood of pawn recovery. Recall that in the control group the client's subjective probability of recovery is on average 93\%, while actual recovery is just 44\%. A further piece of evidence consistent with underestimating negative income shocks is that a large number of people (31\%) in the control group pay a positive amount toward pawn recovery but end up losing their pawn anyway.
